\TheTitle

### 2015-08-15 linvis.tex
Core Model and Implementation Details: Starting section
I've started talking about the core model and the implementation details of the
system. I've commented out the design section.

\section{Model}

\section{Design}

The goal is to build a system that allows users to easily navigate and
understand the changes within the kernel. To do this, the user must have the
ability to perform searches

The goal was to build a system that would allow users to easily navigate the
commit information of

Our primary focus was looking for a way to remove as much unnecessary
information as possible narrow the results.

information as
possible to narrow the results that we wanted to return. Right now, the largest
set of data that a search could return is the entire set of commits that
pertain to a given release. While this set is massive, it pales in comparison
to every commit and merge generated for all versions of the kernel. From there,
the design is centered around the merge tree. These are all of the commits and
merges that eventually are merged by a top-level merge into the kernel. The
design centers around a vine-shape. The top-level merges form a linked list,
each node being a logical section within the kernel. These sections are defined
by Linus. Within each of these top-level merges is a tree of merges and
commits. The merges form the inner-nodes, and the commits form the leaf-nodes.

\evantodo{Make a vine diagram}
% \begin{figure}[h!]
% 	\centering
% 	\includegraphics[width=0.47\textwidth]{figures/empty.png}
% 	\caption{}
% 	\label{}
% \end{figure}

Different kinds of users need to be able to use the tool differently.
Some users may be looking for a top-down approach, trying to find the merge
closest to the top-level merge that works with a given set of files. Other uses
may be looking for a bottom-up approach, given a commit, what top-level merge
includes this commit. Other users are interested in what happens in a given
release cycle without any other requirements.

\subsection{Architecture}

% Database
We split the data presented among five tables; commits, filesmod, logs,
pathtomerge, and releases. The commits table stores the metadata about a given
commit or merge. This includes the author, the authored date, the committer,
commit date, and the file-level diff. The filesmod table stores the information
about the files modified in a commit. We have the commit id, or cid, of the
commit, the filename, the number of lines added and the number of lines removed
from the file. There may be multiple files within a given commit, and there may
be multiple commits editing the same file, the database uses an index as the
primary key, though the primary key could be the cid, filename pair.

% Tables
% commits
% filesmod
% logs
% pathtomerge
% releases

@@

\subsection{Navigation}

A user is greeted by the search screen. We break the kernel down by release,
limiting the maximum information a user can query to help minimize being
overwhelmed. From there, users can either search by author name, commit id, or
keyword from the log preview. A user may also request the top-level merges that
meet the requirements. If the checkbox is unchecked, a user is able to query
all commits and merges that happened in the selected release cycle. If the box
is checked, the user will get all of the top-level merges in the release cycle
that contain a commit or merge that match the given criteria. If no criteria
are provided and the box is checked, the user will simply be given all
top-level merges for that release cycle. This helps separate the use-cases,
allowing users wanting the bottom-up approach to perform searches, and users
wanting a top-down approach to perform searches.

Once a user has found either the top-level merge or commit that they are
interested in, they should be able to move freely between the commits and
merges in the tree. We use three mechanisms to provide better navigation
through the tree. The tree view, the list tree, and breadcrumbs.

The tree view provides most of the
navigational functionality, allowing users to jump to any commit or merge in
the current tree. The main tree view displays all the commits and merges, the
root is the top-level merge of all the commits and merges in the group. Users
are able to see all commits and merges of all the merges.

\evantodo{Picture of tree}
% \begin{figure}[h!]
% 	\centering
% 	\includegraphics[width=0.47\textwidth]{figures/empty.png}
% 	\caption{}
% 	\label{}
% \end{figure}

The list tree shows the merges and commits of the current subtree, built as
nested lists of links to the respective commits and merges. The information in
this tree is a subset of the main tree view, providing a method users with a
view of what commits and merges are below the current commit or merge. If the
current position is a commit, the tree will be empty, as commits are leaf
nodes in the tree representation. This is designed for letting users move
quickly down in the tree.

\evantodo{Picture of list tree}
% \begin{figure}[h!]
% 	\centering
% 	\includegraphics[width=0.47\textwidth]{figures/empty.png}
% 	\caption{}
% 	\label{}
% \end{figure}

The breadcrumbs show the path of merges that are above the current commit or
merge, up to the top-level merge. This allows users a fast way to move up in
the tree.

\evantodo{Picture of breadcrumbs}
% \begin{figure}[h!]
% 	\centering
% 	\includegraphics[width=0.47\textwidth]{figures/empty.png}
% 	\caption{}
% 	\label{}
% \end{figure}

\subsection{Information and Presentation}

Navigation is only effective if the destination contains the desired
information. We present the commit log, what files were edited, and what
modules were edited at a given commit or merge. Normal tools are unable to
provide information about what files are edited in a merge because they do no
use the tree structure. From our tree structure, we are able to traverse the
subtree, making note of what files are edited and how many lines of code are
added and removed at every commit.

\evantodo{Picture of files}
% \begin{figure}[h!]
% 	\centering
% 	\includegraphics[width=0.47\textwidth]{figures/empty.png}
% 	\caption{}
% 	\label{}
% \end{figure}

The tree views provide navigation, but are also able to present implied
information about the depth and number of commits in a given merge.

\section{Discussion}

Our search provides mechanisms for users looking for top-down and bottom-up
approaches. In figures \ref{fig:AndrewMortonMerges} and \ref{fig:AndrewMorton}
we see the difference in responses when looking for the merges by Linus and the
commits authored by Andrew Morton.
\evantodo{Picture of results for top-down and bottom-up}

%% http://localhost:8080/search?version=Linux+3.14&commit_date_begin=&commit_date_end=&search-text=Morton&search-type=Author&merges=on

% \begin{figure}[h!]
% 	\centering
% 	\includegraphics[width=0.47\textwidth]{figures/empty.png}
% 	\caption{}
% 	\label{fig:AndrewMortonMerges}
% \end{figure}
%
% \begin{figure}[h!]
% 	\centering
% 	\includegraphics[width=0.47\textwidth]{figures/empty.png}
% 	\caption{}
% 	\label{fig:AndrewMorton}
% \end{figure}

>>>>

\section{Core Model}
Each merge may contain zero or more children of other merges or commits.
Commits have no children, and therefore are always leaf nodes, but commits
contain information about what files are edited, how many lines are edited, and
other important information.

Core Model:
	Merges are inner nodes
	Commits are leaf nodes

\section{Implementation Details}

We built a we-based tool to provide information about the kernel.
We chose to use Nginx as the main web server, postgresql as the dbms, and Flask
as the framework for generating the dynamic content.

Nginx is a high-performance, scalable HTTP and mail server. Started in 2002,
the project is much younger than the Apache project, and designed with massive
scalability and multi-processing in mind. Instead of using request-driven
threading, Nginx uses an event-driven architecture, making it more scalable,
proving itself as being the web server behind Netflix, Hulu, GitHub, Tumblr,
and many other popular sites.

Postgresql is our dbms of choice, providing fast and reliable results. There
are multiple reasons behind choosing postgresql over another dbms. The main
reason being that the dataset provided from \evantodo{paper} was generated from
a postgresql database, allowing us to import the data directly without any
further conversions. The secondary reason is that we are more familiar with
postgresql than the other systems available.

We chose the python micro-framework Flask for generating the dynamic content.
Working with flask is simple and easy.

Tool Implementation Details:
	Web Server: Nginx, Flask, postgresql
	Database: 5 tables

% \section{Design}

@@

% The goal is to build a system that allows users to easily navigate and
% understand the changes within the kernel. We provide a mechanism for performing
% searches to filter out irrelevant commits and merges, and only work with
% information that they are interested in. At the top level, the commits are
% grouped by release version. \evan{We currently do not provide a mechanism for
% checking real versions and release candidates\ldots Might be useful to at least
% note in search results section}.
% information as
% possible to narrow the results that we wanted to return. Right now, the largest
% set of data that a search could return is the entire set of commits that
% pertain to a given release. While this set is massive, it pales in comparison
% to every commit and merge generated for all versions of the kernel. From there,
% the design is centered around the merge tree. These are all of the commits and
% merges that eventually are merged by a top-level merge into the kernel. The
% design centers around a vine-shape. The top-level merges form a linked list,
% each node being a logical section within the kernel. These sections are defined
% by Linus. Within each of these top-level merges is a tree of merges and
% commits. The merges form the inner-nodes, and the commits form the leaf-nodes.
% \evantodo{Make a vine diagram}
% % \begin{figure}[h!]
% % 	\centering
% % 	\includegraphics[width=0.47\textwidth]{figures/empty.png}
% % 	\caption{}
% % 	\label{}
% % \end{figure}
% Different kinds of users need to be able to use the tool differently.
% Some users may be looking for a top-down approach, trying to find the merge
% closest to the top-level merge that works with a given set of files. Other uses
% may be looking for a bottom-up approach, given a commit, what top-level merge
% includes this commit. Other users are interested in what happens in a given
% release cycle without any other requirements.
% \subsection{Architecture}
% % Database
% We split the data presented among five tables; commits, filesmod, logs,
% pathtomerge, and releases. The commits table stores the metadata about a given
% commit or merge. This includes the author, the authored date, the committer,
% commit date, and the file-level diff. The filesmod table stores the information
% about the files modified in a commit. We have the commit id, or cid, of the
% commit, the filename, the number of lines added and the number of lines removed
% from the file. There may be multiple files within a given commit, and there may
% be multiple commits editing the same file, the database uses an index as the
% primary key, though the primary key could be the cid, filename pair.
% % Tables
% % commits
% % filesmod
% % logs
% % pathtomerge
% % releases
% %
% \subsection{Navigation}
% A user is greeted by the search screen. We break the kernel down by release,
% limiting the maximum information a user can query to help minimize being
% overwhelmed. From there, users can either search by author name, commit id, or
% keyword from the log preview. A user may also request the top-level merges that
% meet the requirements. If the checkbox is unchecked, a user is able to query
% all commits and merges that happened in the selected release cycle. If the box
% is checked, the user will get all of the top-level merges in the release cycle
% that contain a commit or merge that match the given criteria. If no criteria
% are provided and the box is checked, the user will simply be given all
% top-level merges for that release cycle. This helps separate the use-cases,
% allowing users wanting the bottom-up approach to perform searches, and users
% wanting a top-down approach to perform searches.
% Once a user has found either the top-level merge or commit that they are
% interested in, they should be able to move freely between the commits and
% merges in the tree. We use three mechanisms to provide better navigation
% through the tree. The tree view, the list tree, and breadcrumbs.
% The tree view provides most of the
% navigational functionality, allowing users to jump to any commit or merge in
% the current tree. The main tree view displays all the commits and merges, the
% root is the top-level merge of all the commits and merges in the group. Users
% are able to see all commits and merges of all the merges.
% \evantodo{Picture of tree}
% % \begin{figure}[h!]
% % 	\centering
% % 	\includegraphics[width=0.47\textwidth]{figures/empty.png}
% % 	\caption{}
% % 	\label{}
% % \end{figure}
% The list tree shows the merges and commits of the current subtree, built as
% nested lists of links to the respective commits and merges. The information in
% this tree is a subset of the main tree view, providing a method users with a
% view of what commits and merges are below the current commit or merge. If the
% current position is a commit, the tree will be empty, as commits are leaf
% nodes in the tree representation. This is designed for letting users move
% quickly down in the tree.
% \evantodo{Picture of list tree}
% % \begin{figure}[h!]
% % 	\centering
% % 	\includegraphics[width=0.47\textwidth]{figures/empty.png}
% % 	\caption{}
% % 	\label{}
% % \end{figure}
% The breadcrumbs show the path of merges that are above the current commit or
% merge, up to the top-level merge. This allows users a fast way to move up in
% the tree.
% \evantodo{Picture of breadcrumbs}
% % \begin{figure}[h!]
% % 	\centering
% % 	\includegraphics[width=0.47\textwidth]{figures/empty.png}
% % 	\caption{}
% % 	\label{}
% % \end{figure}
% \subsection{Information and Presentation}
% Navigation is only effective if the destination contains the desired
% information. We present the commit log, what files were edited, and what
% modules were edited at a given commit or merge. Normal tools are unable to
% provide information about what files are edited in a merge because they do no
% use the tree structure. From our tree structure, we are able to traverse the
% subtree, making note of what files are edited and how many lines of code are
% added and removed at every commit.
% \evantodo{Picture of files}
% % \begin{figure}[h!]
% % 	\centering
% % 	\includegraphics[width=0.47\textwidth]{figures/empty.png}
% % 	\caption{}
% % 	\label{}
% % \end{figure}
% The tree views provide navigation, but are also able to present implied
% information about the depth and number of commits in a given merge.
% \section{Discussion}
% Our search provides mechanisms for users looking for top-down and bottom-up
% approaches. In figures \ref{fig:AndrewMortonMerges} and \ref{fig:AndrewMorton}
% we see the difference in responses when looking for the merges by Linus and the
% commits authored by Andrew Morton.
% \evantodo{Picture of results for top-down and bottom-up}
% %% http://localhost:8080/search?version=Linux+3.14&commit_date_begin=&commit_date_end=&search-text=Morton&search-type=Author&merges=on
% % \begin{figure}[h!]
% % 	\centering
% % 	\includegraphics[width=0.47\textwidth]{figures/empty.png}
% % 	\caption{}
% % 	\label{fig:AndrewMortonMerges}
% % \end{figure}
% %
% % \begin{figure}[h!]
% % 	\centering
% % 	\includegraphics[width=0.47\textwidth]{figures/empty.png}
% % 	\caption{}
% % 	\label{fig:AndrewMorton}
% % \end{figure}
